---
title: "IMDb Node Importance Measures"
output: html_notebook
---

This script aims at doing a first rudimentary analysis of node importance measure results on the IMDb actors 2011 datasets.
This includes extracting the top 20 actors according to each measure and plotting the distribution of each measure.

### 1. Load Node Importance Measure and Meta Data
```{r}
bc = read.csv("../results/networkit_betweenness_centrality_hollywood-2011.txt", sep="\t", header = FALSE)
colnames(bc) <- c("ID", "BC")

cc = read.csv("../results/networkit_closeness_centrality_hollywood-2011.txt", sep="\t", header = FALSE)
colnames(cc) <- c("ID", "CC")

pr = read.csv("../results/networkit_pagerank_hollywood-2011.txt", sep="\t", header = FALSE)
colnames(pr) <- c("ID", "PR")

id_mapping = read.csv("../results/hollywood-2011-ids.txt", header=FALSE)
colnames(id_mapping) <- c("ID", "Name")

# transform ids to be 1-indexed to be able to work easily with them in R
bc$ID <- bc$ID + 1
cc$ID <- cc$ID + 1
pr$ID <- pr$ID + 1
id_mapping$ID <- id_mapping$ID + 1

# find actor / actress with highest betweenness centrality
max_bc <- bc[which.max(bc$BC),]
max_bc_actor <- id_mapping[max_bc$ID,]
max_bc_actor

library(dplyr)
top.vertices <- bc %>% slice_max(BC, n=20)
top.vertices[order(top.vertices$BC, decreasing = TRUE),]

id_mapping[964355,]
id_mapping[368965,]
id_mapping[1757679,]
id_mapping[579600, ]

id_mapping[top.vertices[order(top.vertices$BC, decreasing = TRUE),]$ID,]

id_mapping[id_mapping$Name == "Hitler, Adolf",]

```

### 2. Find top 20 actors according to each measure

#### PageRank

```{r}
library(dplyr)
pr.top.vertices <- pr %>% slice_max(PR, n=20)
pr.top.vertices <- pr.top.vertices[order(pr.top.vertices$PR, decreasing = TRUE),]

pr.top.actors <- id_mapping[pr.top.vertices[order(pr.top.vertices$PR, decreasing = TRUE),]$ID,]
pr.top.actors <- cbind(pr.top.actors, pr.top.vertices)
pr.top.actors
```


#### Betweenness Centrality

```{r}
library(dplyr)
bc.top.vertices <- bc %>% slice_max(BC, n=20)
bc.top.vertices <- bc.top.vertices[order(bc.top.vertices$BC, decreasing = TRUE),]

bc.top.actors <- id_mapping[bc.top.vertices[order(bc.top.vertices$BC, decreasing = TRUE),]$ID,]
bc.top.actors <- cbind(bc.top.actors, bc.top.vertices)
bc.top.actors
```
#### Closeness Centrality

```{r}
library(dplyr)
cc.top.vertices <- cc %>% slice_max(CC, n=20)
cc.top.vertices <- cc.top.vertices[order(cc.top.vertices$CC, decreasing = TRUE),]

cc.top.actors <- id_mapping[cc.top.vertices[order(cc.top.vertices$CC, decreasing = TRUE),]$ID,]
cc.top.actors <- cbind(cc.top.actors, cc.top.vertices)
cc.top.actors
```


#### Overlaps - Actors that are important according to two or all measures

```{r}
pr.top.actors.names <- pr.top.actors$Name
bc.top.actors.names <- bc.top.actors$Name
cc.top.actors.names <- cc.top.actors$Name

overlap.pr.bc <- intersect(pr.top.actors.names,bc.top.actors.names)
overlap.pr.cc <- intersect(pr.top.actors.names,cc.top.actors.names)
overlap.cc.bc <- intersect(bc.top.actors.names,cc.top.actors.names)

in.all.three <- Reduce(intersect, list(pr.top.actors.names,bc.top.actors.names,cc.top.actors.names))
```

Why do measures obtain similar results? 
-> all measures build upon connections to other vertices, if you have a lot of connections thats always good for you => what is the degree centrality of top vertices is there a correlation between degree centrality 
- BC <-> CC <- if you are on many shortest paths, it's probable that you are close to many vertices
- BC <-> PR <- Highest overlap, interesting

### 3. Score Distributions

#### PageRank -> undirected, measure of connectedness?
```{r}
pr.max <- max(pr$PR)
hist(pr$PR, breaks = 200, xlim=range(0,pr.max))
hist(pr$PR, breaks = 200, xlim=range(0,0.000001))
hist(pr$PR, breaks = 200, xlim=range(0,0.00001))
```
#### PageRank
```{r}
bc.max <- max(bc$BC)
hist(bc$BC, breaks = 200, xlim=range(0,bc.max))
hist(bc$BC, breaks = 10000000, xlim=range(0,100000))
```
```{r}
summary(bc$BC)
```

- BC differentiates very strongly -> 50% of vertices have a value of 0 / no shortest path goes over them, difference of values is very high - max value is 23 452 180 770.


```{r}
cc.max <- max(cc$CC)
hist(cc$CC, breaks = 200, xlim=range(0,cc.max))
hist(cc$CC, breaks = 10000000, xlim=range(0,100000))
```

How do I interpret CC value?
0.3 


### Difference CC and BC

- see Robins Sketch -> BC is a "winner-takes-it-all" approach, so close nodes can have 0 vs. big value BC scores
- CC disstributes more evenly - close neighbors have similar scores